---
title: "Re-analysis of Ritchie, Bates, Deary et al."
output: github_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
library("lavaan")
library('lavaanPlot')
knitr::opts_chunk$set(echo = TRUE)
```

## Load in the data

```{r}
input_mat = '
1											
0.42	1										
0.43	0.31	1									
0.44	0.3	0.31	1								
0.46	0.31	0.33	0.37	1							
0.46	0.31	0.28	0.39	0.57	1						
0.32	0.22	0.48	0.24	0.31	0.27	1					
0.47	0.27	0.33	0.62	0.45	0.48	0.22	1				
0.45	0.25	0.4	0.41	0.44	0.4	0.3	0.45	1			
0.42	0.21	0.3	0.3	0.4	0.34	0.27	0.34	0.54	1		
0.28	0.14	0.24	0.31	0.38	0.4	0.16	0.41	0.42	0.32	1	
0.67	0.39	0.46	0.49	0.58	0.51	0.35	0.53	0.51	0.4	0.36	1'
input_names = c("Age11_MHT","Edu","LM","DSS","MR","BD","VPA","SS","LNS","DSB","SpSp","Age70_MHT")
cor_mat = getCov(input_mat, names = input_names, lower=T, diag=T  )
ntotal = 1028
```

## Fit and confirm the published models

"*Using modification indexes calculated in Mplus, we found five residual covariances that were significant in the baseline model. Four of these described clear content overlap in the tests (between Matrix Reasoning and Block Design, Logical Memory and Verbal Paired Associates, Digit-Symbol and Symbol Search, Digit Span Backwards and Letter-Number Sequencing) and one was unexpectedly negative (between the MHT and Spatial Span).*"

```{r}
# ---
EduOnlyG.model <- '
g_adult =~ Age70_MHT + LM + DSS + MR + BD + VPA + SS + LNS + DSB + SpSp
g_adult + Edu ~ Age11_MHT
g_adult ~ Edu
Age70_MHT ~~ SpSp
MR ~~ BD
LM ~~ VPA
DSS ~~ SS
DSB ~~ LNS'

EduGandS.model <- '
g_adult =~ Age70_MHT + LM + DSS + MR + BD + VPA + SS + LNS + DSB + SpSp
g_adult + Edu ~ Age11_MHT
g_adult + DSS + LM ~ Edu
Age70_MHT ~~ SpSp
MR ~~ BD
LM ~~ VPA
DSS ~~ SS
DSB ~~ LNS'

EduOnlyS.model <- '
g_adult =~ Age70_MHT + LM + DSS + MR + BD + VPA + SS + LNS + DSB + SpSp
g_adult + Edu ~ Age11_MHT
Age70_MHT + LM + DSS + MR + BD + VPA + SS ~ Edu
MR ~~ BD
LM ~~ VPA
DSS ~~ SS
DSB ~~ LNS
Age70_MHT ~~ SpSp'

EduOnlyG.fit <- cfa(EduOnlyG.model, sample.cov = cor_mat , sample.nobs = ntotal , std.lv = T )
EduOnlyS.fit <- cfa(EduOnlyS.model, sample.cov = cor_mat , sample.nobs = ntotal , std.lv = T )
EduGandS.fit <- cfa(EduGandS.model, sample.cov = cor_mat , sample.nobs = ntotal , std.lv = T )

cat("Model 1" , fitMeasures(EduOnlyG.fit,c("rmsea","aic")),'\n')
cat("Model 2" , fitMeasures(EduGandS.fit,c("rmsea","aic")),'\n')
cat("Model 3" , fitMeasures(EduOnlyS.fit,c("rmsea","aic")),'\n')

cat ("dAIC Only S vs. G and S" , fitMeasures(EduOnlyS.fit,"aic") - fitMeasures(EduGandS.fit,"aic") , '\n' )
cat ("dAIC Only S vs. Only G" , fitMeasures(EduOnlyS.fit,"aic") - fitMeasures(EduOnlyG.fit,"aic") , '\n' )

```
We confirm the lower (better) AIC for a model with paths only on S compared to a model with paths to g and S, and much lower AIC for a model only on g.

"*We then compared Model C to the previous models. It had significantly better fit than both Model A, ΔAIC = 19.08, χ2(6) = 31.08, p < .001; and Model B, ΔAIC = 9.90, χ2(4) = 17.90, p = .001.*"

## Plot Model 1 : Only on g
```{r}
lavaanPlot( model = EduOnlyG.fit , coefs=T , stand=T )
```
## Plot Model 2 : On g and s
```{r}
lavaanPlot( model = EduGandS.fit , coefs=T , stand=T )
```
## Plot Model 3 : Only on s
```{r}
lavaanPlot( model = EduOnlyS.fit , coefs=T , stand=T )
```

## Do model selection for Model 2
```{r}

# start without the effect of Edu on S

EduGandS.baseline <- '
g_adult =~ Age70_MHT + LM + DSS + MR + BD + VPA + SS + LNS + DSB + SpSp
g_adult + Edu ~ Age11_MHT
Age70_MHT ~~ SpSp
MR ~~ BD
LM ~~ VPA
DSS ~~ SS
DSB ~~ LNS'

all_vals = c("LM","DSS","MR","BD","VPA","SS","LNS","DSB","SpSp","Age70_MHT")
min_p = NA
included_vals = "g_adult"
# Iterate until no more significant paths
while( is.na(min_p) | min_p < 0.05 ) {
  # Iterate through all specific tests
  min_p = 1
  for ( i in 1:length(all_vals) ) {
      new_vals = c(included_vals,all_vals[i])
      eqn = paste(paste(new_vals,collapse=" + ")," ~ Edu",sep='')
      new_model = paste(EduGandS.baseline,'\n',eqn,sep='')
      EduGandS.fit <- cfa(new_model, sample.cov = cor_mat , sample.nobs = ntotal , std.lv = T)
      coefs = standardizedSolution(EduGandS.fit)
      cur_pv = coefs[coefs$lhs == all_vals[i] & coefs$op == "~" & coefs$rhs == "Edu","pvalue"]
      if ( cur_pv < min_p ) {
        min_val = all_vals[i]
        min_p = cur_pv
      }
  }
  
  # if there's a significant path, add it
  cat(min_val,min_p,'\n')
  if ( min_p < 0.05 ) {
    included_vals = c(included_vals,min_val)
    all_vals = setdiff(all_vals,min_val)
  }
  cat('\n')
}

# print final model
cat( "Final specific paths:" , included_vals , '\n' )
```
Interestingly, SpSp was the first selected path and highly significant. LM and DSS were included as paths in Ritchie et al. but SpSp was not (reasons unstated).

Now let's test the relative model fit.

```{r}
EduGandS_new.model <- '
g_adult =~ Age70_MHT + LM + DSS + MR + BD + VPA + SS + LNS + DSB + SpSp
g_adult + Edu ~ Age11_MHT
g_adult + DSS + LM + SpSp ~ Edu
Age70_MHT ~~ SpSp
MR ~~ BD
LM ~~ VPA
DSS ~~ SS
DSB ~~ LNS'

EduGandS_new.fit <- cfa(new_model, sample.cov = cor_mat , sample.nobs = ntotal , std.lv = T)
cat ("dAIC Only S vs. G and S (updated)" , fitMeasures(EduOnlyS.fit,"aic") - fitMeasures(EduGandS_new.fit,"aic") , '\n' )
```

The updated model fits better than the model only on S. Let's visualize it:

```{r}
lavaanPlot( model = EduGandS_new.fit , coefs=T , stand=T )
```
There's a significant positive path from Edu to g, and a negative path from Edu to SpSp. Let's look at the stanardized coefficients:

```{r}
standardizedSolution(EduGandS.fit)
```

## Sensitivity analysis: Remove SpSp entirely from the analysis

```{r}
EduOnlyG.model <- '
g_adult =~ Age70_MHT + LM + DSS + MR + BD + VPA + SS + LNS + DSB
g_adult + Edu ~ Age11_MHT
g_adult ~ Edu
MR ~~ BD
LM ~~ VPA
DSS ~~ SS
DSB ~~ LNS'

EduGandS.model <- '
g_adult =~ Age70_MHT + LM + DSS + MR + BD + VPA + SS + LNS + DSB
g_adult + Edu ~ Age11_MHT
g_adult + DSS + LM ~ Edu
MR ~~ BD
LM ~~ VPA
DSS ~~ SS
DSB ~~ LNS'

EduOnlyS.model <- '
g_adult =~ Age70_MHT + LM + DSS + MR + BD + VPA + SS + LNS + DSB
g_adult + Edu ~ Age11_MHT
Age70_MHT + LM + DSS + MR + BD + VPA + SS ~ Edu
MR ~~ BD
LM ~~ VPA
DSS ~~ SS
DSB ~~ LNS'

EduOnlyG.fit <- cfa(EduOnlyG.model, sample.cov = cor_mat , sample.nobs = ntotal , std.lv = T )
EduOnlyS.fit <- cfa(EduOnlyS.model, sample.cov = cor_mat , sample.nobs = ntotal , std.lv = T )
EduGandS.fit <- cfa(EduGandS.model, sample.cov = cor_mat , sample.nobs = ntotal , std.lv = T )

cat("Model 1" , fitMeasures(EduOnlyG.fit,c("rmsea","aic")),'\n')
cat("Model 2" , fitMeasures(EduGandS.fit,c("rmsea","aic")),'\n')
cat("Model 3" , fitMeasures(EduOnlyS.fit,c("rmsea","aic")),'\n')

fitMeasures(EduOnlyS.fit,"aic") - fitMeasures(EduGandS.fit,"aic")
fitMeasures(EduOnlyS.fit,"aic") - fitMeasures(EduOnlyG.fit,"aic")
```
The model with Edu paths to g and S still fits better than a model with only paths to S. Moreover, the model with paths only to g now has approximately the same fit as the model with paths only to S. All of the primary results were apparently driven by the inclusion of SpSp.